Time Series Analysis with Bandt \& Pompe Symbolization and a Test for White Noise in the Entropy-Complexity Plane

### 2021-10-25 Reports/Journal - Confidence Regions/Response-R1.tex

\addtocounter{section}{2}
\addtocounter{subsection}{1}
\addtocounter{subsubsection}{1}
\addtocounter{figure}{11}
The reviewer rises a very relevant question: is the Statistical Complexity needed?
Several researchers have addressed this question, and the unanimous answer is yes, it is needed.
The discussion has been limited to the Physics literature, most markedly after the work by \citet{SimpleMeasureforComplexity} and the subsequent discussion \citep{CommentIonSimpleMeasureforComplexity,CommentIIonSimpleMeasureforComplexity} and rejoinder \citep{ReplytoCommentsonSimpleMeasureforComplexity} papers.

Going further in this direction would require introducing several concepts which may seem unfamiliar to this journal's readership.
Nevertheless, being an relevant point, we opted for illustrating the need of both descriptors, entropy and complexity, with an example in the discussion of the test power.

We split the power subsection in two, and added another study which illustrates the need of considering the complexity:
\begin{quote}
	\subsubsection{$H_1$: Patch of Deterministic Function}

Consider the times series of length $T$ comprised of $T-[c100]$ white noise observations $x_1,x_2,\dots, x_{T-[c100]}$ followed by the signal $y_{T-[c100]+1}, y_{T-[c100]+2}, \dots, y_T$, in which $0\leq c \ll 1$ is the percentage of contamination.
We will verify the behavior of our test for the case $T=1000$, and $y_t$ an increasing function on $t$.
Fig.~\ref{Fig:PointsPatchedIncreasingFunction} shows the effect of such contamination on the white noise time series whose point in the $H\times C$ plane appears in black.
The Figure also shows the confidence region at \SI{99}{\percent}.

@@

	\begin{figure}[hbt]
		\centering
		\includegraphics[width=.7\linewidth]{Figures/PointsPatchedIncreasingFunction}
		\caption{Effect of patching an increasing function at different levels to a white noise sequence.}\label{Fig:PointsPatchedIncreasingFunction}
	\end{figure}

At all levels of contamination, the original point is displaced to a region with smaller entropy and larger complexity.
When the percentage of contamination is below approximately \SI{2}{\percent}, the test will not reject the null hypothesis at the \SI{1}{\percent} level of significance; in fact, the $p$-value is of around \SI{1.5}{\percent} for $c=0,0.01,0.02$.
The $p$-value falls to orders of $10^{-6}$ when the contamination is of \SI{3}{\percent} and above.

### 2021-10-25 Reports/JOURNAL - Confidence Regions/IT-ConfidenceRegionsR1.tex
Ready for first round with authors

At all levels of contamination, the original point is displaced to a region with smaller entropy and larger complexity.
When the percentage of contamination is below approximately \SI{2}{\percent}, the test will not reject the null hypothesis at the \SI{99}{\percent}; in fact, the $p$-value is of around \SI{1.5}{\percent} for $c=0,0.01,0.02$.
The $p$-value falls to orders of $10^{-6}$ when the contamination is of \SI{3}{\percent} and above.

>>>>

At all levels of contamination, the original point is displaced to a region with smaller entropy and larger complexity.
When the percentage of contamination is below approximately \SI{2}{\percent}, the test will not reject the null hypothesis at the \SI{1}{\percent} level of significance; in fact, the $p$-value is of around \SI{1.5}{\percent} for $c=0,0.01,0.02$.
The $p$-value falls to orders of $10^{-6}$ when the contamination is of \SI{3}{\percent} and above.
